NEED TITLE

### 2014-09-30 ms.tex
Added ang mom graphs, mass caption, and discussion on vr/vrms

These simulations display much more complicated dynamics than is captured by the simple analytic theory of Murray and Chang 2014.  In spite of this, we compare radially averaged profiles around these high density points to their analytic theory.  In the left panel of Figure \ref{fig:good_rho_example}, we show the radial density profile around one such high density point. As this figure shows, the radial density profile follows a $r^{-3/2}$ power law in agreement with analytic expections.  This power-law breaks down at small radii, but this is not unexpected as this radii corresponds to the presents of a rotationally support disk.  Such good agreement is not universal for all high density points as shown in the right panel of Figure \ref{fig:bad_rho_example}.  Here the radial density profile follows a $r^{-2}$ power law.  
\begin{figure*}
\plottwo{Track_0256_000_rho.png}{Track_0132_000_rho.png}
\caption{Density as a function of radial position from maximum density point.  The density reaches a maximum of $10^6$ times mean density at $r \approx 10^{-3}$ pc and decline to approximately mean density at $r\approx 3$ pc.  The three straight solid lines are $r^{-3/2}$, $r^{-2}$, and $r^{-5/2}$ power laws. \label{fig:good_rho_example}}
\end{figure*}

@@

In Figure \ref{fig:vr_example}, we plot $v_r$ (blue line) and $v_{\rm rms}$ (green line) as a function of $r$.  In the left panel, the radial velocity curve is sporadic, but the general trend is that $v_r$ declines in toward $0.1$ pc, but then rises inward of this point.  Plotted in red is a $r^{-1/2}$ power law and this inward rise appears to follow this general trend.  The turbulent velocity is smoother, but it follows the general trend of the $v_r$ curve in that it falls slowly inward toward $]\approx 0.1 $ pc before rising inward of that, roughly tracking the $r^{-1/2}$ power law.  These general trends are in rough agreement with our analytic expectations.

@@

\begin{figure*}
\plottwo{Track_0256_000_mass.png}{Track_0132_000_mass.png}
\caption{WRITE CAPTION: Radial velocity, $v_r$ (blue line), and turbulent velocity, $v_{\rm rms}$ (green line) as a function of radial position from maximum density point.  A $r^{-1/2}$ power law is shown as a red line. \label{fig:mass_example}}
\end{figure*}

>>>>

These simulations display much more complicated dynamics than is captured by the simple analytic theory of Murray and Chang 2014.  In spite of this, we compare radially averaged profiles around these high density points to their analytic theory.  In the left panel of Figure \ref{fig:good_rho_example}, we show the radial density profile around one such high density point. As this figure shows, the radial density profile follows a $r^{-3/2}$ power law in agreement with analytic expections.  This power-law breaks down at small radii, but this is not unexpected as this radii corresponds to the presents of a rotationally support disk.  Such good agreement is not universal for all high density points as shown in the right panel of Figure \ref{fig:bad_rho_example}.  Here the radial density profile follows a $r^{-2}$ power law.  
\begin{figure*}
\plottwo{Track_0256_000_rho.png}{Track_0132_000_rho.png}
\caption{Density as a function of radial position from maximum density point.  The density reaches a maximum of $10^6$ times mean density at $r \approx 10^{-3}$ pc and declines to approximately mean density at $r\approx 3$ pc.  The three straight solid lines are $r^{-3/2}$, $r^{-2}$, and $r^{-5/2}$ power laws. \label{fig:good_rho_example}
{bf\ This discusses left panel only, should we move the discussion outside the caption?}}
\end{figure*}

@@

In Figure \ref{fig:vr_example}, we plot $v_r$ (blue line) and $v_{\rm rms}$ (green line) as a function of $r$.  In the left panel, the radial velocity curve is sporadic, but the general trend is that $v_r$ declines in toward $0.1$ pc, but then rises inward of this point.  Plotted in red is a $r^{-1/2}$ power law and this inward rise appears to follow this general trend.  The turbulent velocity is smoother, but it follows the general trend of the $v_r$ curve in that it falls slowly inward toward $]\approx 0.1 $ pc before rising inward of that, roughly tracking the $r^{-1/2}$ power law.  These general trends are in rough agreement with our analytic expectations.  In the right panel, the radial velocity curve is smoother and increases inwards towards $0.01$ pc, tracking the $r^{-1/2}$ power law fairly closely.  This radial velocity begins to fall inward of $0.01$ pc, possibly due to rotational support from the angular momentum of a disk.  The turbulent velocity in the right panel seems to roughly follow an inverse relationship with the radial velocity.  As with the left panel, however, the turbulent velocity is significantly less volatile than the radial velocity and varies only slightly with $r$.

@@

\begin{figure*}
\plottwo{Track_0256_000_mass.png}{Track_0132_000_mass.png}
\caption{WRITE CAPTION: Mass, $MSun$, as a function of radial position from a local maximum density point.     \label{fig:mass_example}}
\end{figure*}
